Escape Analysis and Specialization in a Tracing JIT

### 2010-09-28 talk/pepm2011/paper.tex
that figures

If we do that for our example trace, the trace looks like this:
\begin{figure}
\includegraphics{figures/step2.pdf}
\end{figure}

XXX the figure is moved elsewhere by latex

Now the lifetime of the remaining allocations no longer crosses the jump, and
we can run our escape analysis a second time, to get the following trace:
\begin{figure}
\includegraphics{figures/step3.pdf}
\end{figure}

XXX the figure is moved elsewhere by latex

@@

To make it possible to enter the loop directly from the intepreter, there
needs to be some additional code that enters the loop by taking as input
arguments what is available to the interpreter, i.e. two instances. This
additional code corresponds to one iteration of the loop, which is thus
peeled off \cite{XXX}:

\begin{figure}
\includegraphics{figures/step4.pdf}
\end{figure}

XXX the figure is moved elsewhere by latex

>>>>

If we do that for our example trace, the trace looks like in Figure~\ref{fig:step2}.

\begin{figure}
\includegraphics{figures/step2.pdf}
\label{fig:step2}
\caption{Shifting the Jump}
\end{figure}

Now the lifetime of the remaining allocations no longer crosses the jump, and
we can run our escape analysis a second time, to get the trace in
Figure~\ref{fig:step3}.

\begin{figure}
\includegraphics{figures/step3.pdf}
\label{fig:step3}
\caption{Removing Allocations a Second Time}
\end{figure}

@@

To make it possible to enter the loop directly from the intepreter, there
needs to be some additional code that enters the loop by taking as input
arguments what is available to the interpreter, i.e. two instances. This
additional code corresponds to one iteration of the loop, which is thus
peeled off \cite{XXX}, see Figure~\ref{fig:step3}.

\begin{figure}
\includegraphics{figures/step4.pdf}
\label{fig:step3}
\caption{A Way to Enter the Loop From the Interpreter}
\end{figure}
